% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{CPD Report}

% Please do not change the subtitle
\subtitle{COMP230 - CPD Tasks}

% Please put your student number in the author field
\author{1507729}

\begin{document}

\maketitle

\section*{Introduction}

The first semester of second year has been incredibly busy and has seen a rather large increase in work that I need to do. This has however given me the opportunity to highlight some areas which I can improve going forward. Some of which is having a stronger team focus and making sure I don't take on too many unnecessary tasks, but I could also stand to be more aware of deadlines and what work should be taking priority.

\section{Don't be afraid of confrontation, as a way of resolving issues.}

I really need to work on not being afraid to speak about issues within our group game project. This should be measurable as feedback during peer assessments, though this could become negative feedback. It's not unreasonable to think that I will stand my ground on certain issues that need to be resolved and that staying silent would otherwise cause problems. This will be important later on as it will prevent feature creep as well as maintain the efficiency of the team. This is something I will be focusing on during the first sprint period as we are going to begin reworking parts of the game and making sure we aren't wasting time and effort will be very important.

\section{Not focusing on the things I find interesting or easy at the expense of doing other work.}

I need to spend more time focusing on tasks that could be blocking others instead of just doing the work that's easy, going forward this should be apparent by preventing anyone including myself from being blocked from completing their tasks, with the main focus being on the group game project. My ability to complete more difficult tasks is the only limiting factor, and being confident enough to tackle complex problems is an important quality for programmers to have. It's important because if I focus too much on one thing and neglect other work, it will cause me problems for my team and myself in the future. This is something I hope to work on in the next semester and then going forward to all future projects.


\section{Try to take on less work, to ensure I complete important tasks to a higher standard.}

I need to spend more time focusing on completing a few tasks to a much higher quality. This should mean that the work I'm doing is to a higher standard and that should be clear in the results that I receive and in feedback from lectures. This should be achievable however I do struggle to refuse helping others, and knowing when to say no I need to focus on my own work will be quite important going forward. This is something that will be very important in going forward as work I am assigned will need to be completed while helping others will not help me finish my work. Going into the next semester this will also be one of my focuses to and should be something I am continually working towards achieving.

\section{Be more engaged with my group project and what other members are working on.}

I would like to be more engaged with my group and the tasks they are trying to complete. This should be clear as I should be able to easily relay what members of my team are working on at any point during production. Being more engaged with my team is quite easily achievable as the only difficulty I can see is having team members show up to interact with. This I feel is important as it will inform the team what tasks are being worked on and not to touch as well as what tasks need to be completed. This is something I will be actively doing once my group returns from holidays and we start doing work and I should show a clear improvement by the end of the first sprint and then any subsequent sprints.


\section{Be more organised about deadlines and work that needs to be done.}

I would like to be more aware of my deadlines and I know how much time I have left to work on certain tasks. I am going to get my hands on a year planner and write out the various deadlines so they are clearly marked, while also marking off which days have passed. I have already ordered the year planner and then using MyFalmouth I will be able to get all the relevant dates for hand-ins. This should help me keep on top of work and spend more time working on relevant tasks, I will have this all set up before the start of second semester ready for the next set of assignments.

\section*{Conclusion}

I believe that I have made great improvements in my commitment to spending time within the studio but also in terms of work ethic and ability. I do recognise that I still have a long way to go in terms of becoming industry ready for programming however, I am already learning the programming and don't feel any additional action is needed currently and I think that I need to spend more time working on making my team working skills better.


\end{document}
